Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-05-09 paper/main.tex
latest version

We study the alignment of dark matter halos with the cosmic web
characterized by the tidal and velocity shear fields. We focus on the
alignment of their shape, angular momentum and peculiar velocities. We  
use a cosmological N-body simulation that allows to study dark matter
halos spanning almost five orders of magnitude in mass
($10^{9}$-$10^{14}$) \hMsun and use spatial scales of
$(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
numerical parameters in our experiments we find that the halo shape
presents the strongest alignment along the smallest tidal eigenvector
,e.g. along filaments and walls, with a signal that gets stronger as
the halo mass increases. In the case of the velocity shear field only
massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
the largest tidal eigenvector; that is perpendicular to filaments and
walls. For the angular momentum we find alignment signals only for
halos more massive than $10^{12}$\hMsun both in the tidal and velocity
shear webs where the preferences are for it to be parallel to the
middle eigenvector; perpendicular to filaments and parallel to
walls. Finally, the peculiar velocities show a strong alignment along
the smallest tidal eigenvector for all halo masses; moving along filaments
and walls. In the velocity shear the same alignment is present but
weaker and only for halos less massive than $10^{12}$\hMsun. Most of
the different signals between the two web descriptions are due to the
fact that the main directions of stronger tidal tension and velocity
shear coincide for halos below $10^{12}$\hMsun but are perpendicular
to each other for halos more massive than this threshold.  Our results
clearly show that the two different algorithms we used to define the
cosmic web describe different physical aspects of non-linear collapse
and should be used in a complementary way to understand the effect of
the cosmic web on galaxy evolution. 
\end{abstract}
\begin{keywords}
methods: numerical, galaxies: haloes, cosmology: theory, dark
matter, large-scale structure of Universe
\end{keywords}

@@

These results can be summarized in three important points:
\begin{itemize}
\item The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
behaviours of no-alignment, alignment or anti-alignment.
\item Halo shape provides a strong alignment signal along filaments
  and sheets, more so for massive haloes.
\item Halo spin tends to be oriented perpendicular to filaments and
parallel to sheets, but it is a weaker than shape alignment.
\end{itemize}

@@

We use two algorithms to define the cosmic web in cosmological N-body
simulations. Both are based on the same algorithmic principle, which
determines locally a symmetric tensor which can be diagonalized to yield
three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
corresponding eigenvectors ${\bf e}_{1}$, ${\bf e}_2$ and ${\bf
 e}_3$. This allows for a local classification into one of the
following four web types: void, sheet, filament and peak depending
on whether the number of eigenvalues larger than a given threshold
$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.

@@

In this paper we compute the cosmic web on cubic grids of two different
resolutions $256^3$ and $512^3$ that roughly correspond
to scales of $1$ and $0.5$h$^{-1}$Mpc, respectively. For the T-Web we
interpolate first the matter density field using a Cloud-In-Cell (CIC)
scheme. Then we smooth using a Gaussian kernel with a spatial variance
equal to the size of one grid cell. This smoothed matter density field is
transformed into Fourier space to solve the Poisson equation and find
the gravitational potential $\phi$. The Hessian is computed using a finite
differences method. Finally, the eigenvalues and eigenvectors are
computed on each grid point.

@@

% We present a simple example to clarify the difference
% between the two ways of finding the smoothed velocity field. Let's consider two
% neighboring CIC cells, one with total mass $m_1 = 10^{11}$\hMsun and
% velocity along $x$ $v_{1x}=0$ km/s and a second cell with mass $m_2 = 10^{10}$\hMsun and $v_{2x}=-10$ km/s. In the case of defining an average value for the
% velocity over these two cells our method finds a result $\bar{v}_x=
% (m_1v_{1x} + m_2v_{2x})/(m_1+m_2)= -0.09$km/s while the method used in
% \cite{Vweb,Libeskind2013} would find
% $\bar{v}_x=(v_{1x}+v_{2x})/2=-5$km/s.

@@

\begin{figure*}
\includegraphics[width=0.8\textwidth]{Fig1.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector in the cosmic
  web; $\hat{e}_1$ (black) defines the direction perpendicular to a wall and
  $\hat{e}_3$ (yellow) indicates the direction along a filament. Each row
  presents one of the three properties studied in this paper: shape (major axis),
  angular momentum and  peculiar velocity. The left (right) column presents the
  results against the Vweb (Tweb). Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid. The thick black
  horizontal line at $0.33$ corresponds to the expected fraction for a
  random vector field. The uncertainty is computed assuming poissonian
  statistics in each mass bin.
\label{fig:preferential}}
\end{figure*}

@@

The shape alignment and the Vweb (upper row, left column) gives a
different perspective. Firstly, there seems to be little evidence
for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
on the grid resolution. Secondly, the alignment at higher masses goes
along the first eigenvector $\hat{e}_{1}$ meaning that they mostly lie
perpendicular to the filaments and sheets. In the discussion section
we clarify this result that at first sight might seem puzzling.

For shape alignment and the Tweb (upper row, right column) we find a strong
preferential alignment along the third eigenvector $\hat{e}_{3}$. This
signal increases steadily with mass and is almost independent of the
grid resolution. At high masses between $70\%$ and $100\%$ of the
halos have their major axis aligned along $\hat{e}_{3}$ which means
that they mostly lie along filaments and sheets.

The angular momentum in the Vweb (middle row, left column) presents 
a signal of alignment along the second eigenvector $\hat{e}_{2}$;
between $45\%$ to $60\%$ of the halos are aligned along that
direction, while there is a minority of halos aligned with
$\hat{e}_{1}$.  There is a clear change in trends around
$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
below that mass range there is no evidence for alignment while at
higher masses all the trends we describe are noticeable. This means
that the angular momentum of halos above $10^{12}\hMsun$ tends to lie
along walls, parallel to the vector $\hat{e}_2$; without any clear
trend for alignment/anti-alignment with respec to filaments.

For the angular momentum alignment and the Tweb (middle row, right
column) we find no evidence for any alignment at low masses $<10^{12}\hMsun$.
At higher masses $>10^{12}\hMsun$ there is a weak signal
of preferential alignment along the first and second eigenvectors;
between $35\%$ to $45\%$ of the halos are aligned with respect to
$\hat{e}_1$ and $\hat{e}_2$. Correspondingly, between $10\%$ to $20\%$
of the halos are aligned along $\hat{e}_{3}$. This means
that most of the halos are perpendicular to the filaments and do not
have a clear alignment with respect to walls.

The peculiar velocities (lower panels) show a weak but consistent
alignment along the third eigenvector $\hat{e}_{3}$ of the Tweb for
all masses below $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
aligned along the first eigenvector $\hat{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the Vweb show the same,
although weaker, trend and only for low mass halos $<10^{12}$.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig2.pdf}
\caption{Median of $|\cos\theta|$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions as a function of halo mass.  The errorbars show the $20$ and $80$ percentiles 
  of the distribution; the
  errors on the median are too small to be noticed in this figure. In the upper (lower) panels
  the angle $\theta$ is measured between the halo major axis and the first (third)
  eigenvector.\label{fig:shape_alignment} }
\end{figure*}

@@

In the case of the Vweb (left column) we have a clear alignment with
respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
values $\muavg\approx 0.8$ well above the expected value of $0.5$ for a
random distribution. With respect to the third eigenvector we measure
an anti-alignment with $\muavg\approx0.3$. For low masses
$<10^{12}\hMsun$ we do not detect any alignment signal. This is
consistent with the PA results of massive halos
perpendicular to filaments and parallel to walls.

The Tweb (right column) shows alignment trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude below than the V-web. In this
case we measure an alignment along the third eigenvector and an
anti-alignment along the first eigenvector. In the latter case at the
highest masses $\muavg\approx 0.8$, while in the former at $\muavg\approx
0.2$. This strong alignment/anti-alignment signal mirrors the
interpretation from the PA results that describe halos lying parallel
both to filaments and walls.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig3.pdf}
\caption{Median of $|\cos\theta|$ quantifying the angular momentum
  alignment for the Vweb (left) and the Tweb (right) for two different
  grid resolutions as a function of halo mass. In the upper (lower)
  panels the angle $\theta$ is measured between the first (third)
  eigenvector and the angular momentum
  vector.\label{fig:spin_alignment}} 
\end{figure*}

We now focus our attention on the angular momentum alignment. Figure
\ref{fig:spin_alignment} shows the results as a function of halo mass
following the same panel layout as in Figure
\ref{fig:shape_alignment}. In all cases we see that these alignment
trends are weaker than the shape alignments. For the Vweb low mass halos
$<10^{12}$\hMsun do not show any preferential alignment with the
cosmic web. Halos more massive than this threshold have their angular
momentum slightly perpendicular to the direction defined by the first
eigenvector and are uncorrelated with the third eigenvector. This translates
into a weak tendency for the angular momentum to lie parallel to walls.

In the case of the Tweb, the alignment for low mass halos $<10^{12}$\hMsun
is also absent. More massive halos present a weak alignment along
first eigenvector and anti-alignment with the third eigenvector. This
provides a quantitative expression of the results derived from the
preferential alignment whereby the angular momentum is weakly
perpendicular to filaments.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig4.pdf}
\caption{Median of $\vert\cos\theta\vert$ quantifying the peculiar velocity
  alignment with the Vweb (left) and the Tweb (right) for two different
  grid resolutions as a function of halo mass. In the upper (lower)
  panels the angle $\theta$ is measured between the first (third)
  eigenvector and a halo's peculiar velocity.
\label{fig:velocity_alignment}}
\end{figure*}

Figure \ref{fig:velocity_alignment} shows the results for peculiar
velocities alignments. In the case of the Vweb, the peculiar
velocities show a weak signal of alignment ($\muavg\approx0.55$)
along the third eigenvector for low masses $<10^{12}$\Msun and a weak
anti-alignment at higher masses. The strength of the alignment also shows
a clear dependency on the grid size used to compute the web.

The Tweb shows a stronger alignment with the third eigenvector at all
masses with $\muavg\approx0.6$ and an anti-alignment with the first
eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
these trends remain basically unchanged at all masses and grid
resolutions, with only minor changes for halos masses $>10^{13}$\hMsun.

@@

Figure \ref{fig:drive} shows the results for the major axes of
the Vweb and Tweb (left and right panels) and the shape major axis,
the angular momentum vector, and the halo peculiar velocity (top, middle
and bottom panels, respectively).  As here we show the average
of the halo population above the lower mass limit imposed, the halo
masses that dominate the statistics are close to this lower limit $~10^{11}\hMsun$.
We show the result for the Tweb and Vweb calculated using the two
available resolutions, but as can be seen in general we find no
significant differences in our results.

Halos with higher circularity and inner density show
a higher alignment with the Vweb major axes.  The opposite is the case
of haloes with higher concentration, spin and triaxiality.  This trend
is also visible in the angular momentum vs. Vweb major axis alignment only
for the concentration and spin, with little differences evidenced by the
other halo properties.  The alignment strengthening is somewhat
reversed when comparing the Vweb with the halo peculiar velocity,
with some evidence for a strengthening with lower circularity and
inner density, and a weakening with spin and triaxiality.

On the right panels the trends can also be readily seen.  The Tweb
vs. major axis alignments are stronger for higher circularity,
concentration and inner density, and weaker for higher spins and
triaxialities.  With respect to the angular momentum, the alignment
is weaker for higher circularities, concentrations, inner densities and
spins, and is only strengthened when the triaxiality is higher.
Not much difference is seen in the Tweb vs. halo peculiar velocity
alignments, being this the only regime where there is a clear difference
in influence of halo properties on the alignments with the Tweb and Vweb;
the latter do show important changes on the lower-left panel.

As can be seen, higher concentrations, circularities and densities,
as well as lower spins and triaxialities, produce a similar effect on the
Tweb vs. major axis alignments to that of diminishing the mass
of the halos.  This has also been detected in other halo properties such
as their clustering amplitude in what has been termed assembly bias
\citep[][e.g.]{Gao2005,Li2008,Lacerna2011} where halos of different
ages and equal mass show different clustering amplitudes, which could
also be interpreted as a change in the effective halo mass according
to halo properties.

An older halo age has been shown to come along with more spherical halo
shapes, higher concentrations and halo inner density.  However, in the
assembly bias scenario of \cite{Gao2005}, these halos tend to show a clustering
amplitude consistent with that of the median halo population of higher masses.
In terms of the alignments with the Tweb, our results show the opposite
trend.  This shows that the physics behind the clustering amplitude and
alignments do not necessarily coincide.  The full understanding of
the dependence of halo properties and/or on their environment is
a complex problem, but these results provide extra information that complements
that obtained from clustering measurements.

@@

For the two algorithms, Tweb and Vweb, we have the information for their
eigenvectors and eigenvalues on exactly the same positions defined
by the grids. This allows us to compute the pair-wise alignment
between the eigenvectors in the two web finders.

@@

Figure \ref{fig:interweb} shows the values for $\muavg$ between the
two $\hat{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
shows that there is an alignment, $\muavg\approx 1.0$, for low mass
halos and an anti-alignment, $\muavg\approx 0.2$ for massive ones.

@@

We have examined the alignment of shape, angular momentum and peculiar
velocity of dark matter halos with respect to the cosmic web. We use
publicly available data from two algorithms implemented on a large
cosmological N-body simulation to study halo populations spanning five
orders of magnitude in mass. The first algorithm uses the tidal field (Tweb)
and the second the velocity shear (Vweb); both include results on
spatial scales of $0.5$\hMpc and $1.0$\hMpc.

We quantify the alignments in two complementary ways. The first one
measures the fraction of halos in a population that is preferentially
aligned with either one of the eigenvectors $\hat{e}_1$, $\hat{e}_2$
or $\hat{e}_3$ in the local definition of the cosmic web. The second
method measures the average value of the angle between an eigenvector
and the quantity of interest. These two measurements give us a
complete picture for the different degrees of alignment in the web.

We find that the strongest alignment occurs for the halo shape with
respect to the Tweb. In this case the halos tend to align with the
third eigenvector, $\hat{e}_3$, meaning that they lie along filaments
and walls. This trend gets stronger as the halo mass
increases and agrees with all the results published so far. Instead,
for the momentum based Vweb, there is only an anti-alignment for halos
more massive than $10^{12}\hMsun$, a result that is presented here for
the first time.

A much weaker alignment signal is present for the angular momentum. In
the Tweb only the most massive halos $>10^{12}$\hMsun are
perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
while for the Vweb the massive halos are aligned with $\hat{e}_2$,
lying along sheets. These results broadly agree with the
published literature. Nevertheless, in some publications
\citep{AragonCalvo2007,Hahn2007,AragonCalvo2014} there is an alignment signal
reported at lower halo masses $<10^{12}$\hMsun that we do not detect
in our measurements. Actually \cite{AragonCalvo2014}, using a
multiscale web-finding method, confirmed the mass $10^{12}$\hMsun as a
transitional scale between alignment /anti-alignment in filaments,
showing that it reflects the degree of evolution of the host
filament.

@@

A new result from our study is the alignment for the peculiar
velocities. Here we find a relatively strong signal of alignment along
the direction defined by the third eigenvector, $\hat{e}_3$, and
perpendicular to the first, $\hat{e}_1$. This signal is clear in the
Tweb for all masses below $<10^{13}$\hMsun. This can be interpreted as
a flow parallel to walls and filaments. In the case of the Vweb
similar signal, albeit weaker, is present only for the low mass halos
$<10^{12}\hMsun$. A similar result was obtained by \citep{Padilla2005}
who found that peculiar velocities are larger in the direction
parallel to void walls.

The different behaviour for the alignments of massive halos in the
Tweb and the Vweb is explained by an anti-alignment between the
eigenvectors in the two web grids for massive halos
$>10^{12}\hMsun$. For low mass halos the directions defined by the two
webs point in the same direction. This trends can be interpreted as
non-linear effects that appear in the two different physical
descriptions for the cosmic web, but the impact of the numerical
choices to build the interpolation must be studied as well.

We also performed a simple study to find evidence of halo properties,
other than mass, in driving the alignments. We find that in the case of
shape, high concentration halos or halos with a low value of
the reduced spin parameter tend to show a stronger signal. This trend is
more pronounced in the Tweb than in the Vweb. Concerning angular
momentum we find that the anti-alignment signal is stronger for halos
with high spin values. In the peculiar velocities we do not find any
effect in the Tweb alignments, and the results for the Vweb show 
wide variations with grid resolution that impedes driving any strong
conclusion.

>>>>

We study the alignment of dark matter halos with the cosmic web
characterized by the tidal and velocity shear fields. We focus on the
alignment of their shape, angular momentum and peculiar velocities. We  
use a cosmological N-body simulation that allows to study dark matter
halos spanning almost five orders of magnitude in mass
($10^{9}$-$10^{14}$) \hMsun and use spatial scales of
$(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
numerical parameters in our experiments we find that the halo shape
presents the strongest alignment along the smallest tidal eigenvector,
e.g. along filaments and walls, with a signal that gets stronger as
the halo mass increases. In the case of the velocity shear field only 
massive halos $>10^{12}$\hMsun tend to have their shapes aligned along
the largest tidal eigenvector; that is perpendicular to filaments and
walls. For the angular momentum we find alignment signals only for
halos more massive than $10^{12}$\hMsun both in the tidal and velocity
shear webs where the preferences are for it to be parallel to the
middle eigenvector; perpendicular to filaments and parallel to
walls. Finally, the peculiar velocities show a strong alignment along
the smallest tidal eigenvector for all halo masses; halos move along filaments
and walls. In the velocity shear the same alignment is present but
weaker and only for halos less massive than $10^{12}\hMsun$. Most of
the different signals between the two web descriptions are due to the
fact that the main directions of stronger tidal tension and velocity
shear coincide for halos below $10^{12}$\hMsun but are perpendicular
to each other for halos more massive than this threshold.  Our results
clearly show that the two different algorithms we used to define the
cosmic web describe different physical aspects of non-linear collapse
and should be used in a complementary way to understand the effect of
the cosmic web on galaxy evolution. 
\end{abstract}
\begin{keywords}
methods: numerical, galaxies: haloes, cosmology: theory, dark
matter, large-scale structure of Universe
\end{keywords}

@@

These results can be summarized in three important points:
\begin{itemize}
\item The halo mass of $1-5\times 10^{12}$\hMsun is a threshold mass between
behaviours of no-alignment, alignment or anti-alignment.
\item Halo shape provides a strong alignment signal along filaments
  and sheets, more so for massive haloes.
\item Halo angular momentum tends to be oriented perpendicular to filaments and
parallel to sheets, but it is weaker than shape alignment.
\end{itemize}

@@

We use two algorithms to define the cosmic web in cosmological N-body
simulations. Both are based on the same algorithmic principle, which
determines locally a symmetric tensor which can be diagonalized to yield
three real eigenvalues $\lambda_1>\lambda_2>\lambda_3$ and their
corresponding eigenvectors $\hat{e}_{1}$, $\hat{e}_2$ and
$\hat{e}_3$. This allows for a local classification into one of the 
following four web types: void, sheet, filament and peak depending
on whether the number of eigenvalues larger than a given threshold
$\lambda_{th}$ is $3$, $2$, $1$ or $0$, respectively.

@@

In this paper we compute the cosmic web on cubic grids of two different
resolutions $256^3$ and $512^3$ that roughly correspond
to scales of $1$ and $0.5\hMpc$, respectively. For the T-Web we
interpolate first the matter density field using a Cloud-In-Cell (CIC)
scheme. Then we smooth using a Gaussian kernel with a spatial variance
equal to the size of one grid cell. This smoothed matter density field is
transformed into Fourier space to solve the Poisson equation and find
the gravitational potential $\phi$. The Hessian is computed using a finite
differences method. Finally, the eigenvalues and eigenvectors are
computed on each grid point.

@@

@@

\begin{figure*}
\includegraphics[width=0.8\textwidth]{Fig1.pdf}
\caption{Fraction of halos in a mass bin that show a preferential
  alignment with respect to an eigenvector in the cosmic
  web; $\hat{e}_1$ (black) defines the direction perpendicular to a wall and
  $\hat{e}_3$ (yellow) indicates the direction along a filament. Each row
  presents one of the three properties studied in this paper: shape (major axis),
  angular momentum and  peculiar velocity. The left (right) column presents the
  results against the V-web (T-web). Strong colors refer to $256^3$ grid
  resolutions and lighter colors to a $512^3$ grid. The thick black
  horizontal line at $0.33$ corresponds to the expected fraction for a
  random vector field. The uncertainty is computed assuming poissonian
  statistics in each mass bin.
\label{fig:preferential}}
\end{figure*}

@@

The shape alignment and the V-web (upper row, left column) give a
different perspective. Firstly, there seems to be little evidence
for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
on the grid resolution. Secondly, the alignment at higher masses goes
along the first eigenvector $\hat{e}_{1}$ meaning that they mostly lie
perpendicular to the filaments and sheets. In the discussion section
we clarify this result that at first sight might seem puzzling.

For shape alignment and the T-web (upper row, right column) we find a strong
preferential alignment along the third eigenvector $\hat{e}_{3}$. This
signal increases steadily with mass and is almost independent of the
grid resolution. At high masses between $70\%$ and $100\%$ of the
halos have their major axis aligned along $\hat{e}_{3}$ which means
that they mostly lie along filaments and sheets.

The angular momentum in the V-web (middle row, left column) presents 
a signal of alignment along the second eigenvector $\hat{e}_{2}$;
between $45\%$ to $60\%$ of the halos are aligned along that
direction, while there is a minority of halos aligned with
$\hat{e}_{1}$.  There is a clear change in trends around
$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
below that mass range there is no evidence for alignment while at
higher masses all the trends we describe are noticeable. This means
that the angular momentum of halos above $10^{12}\hMsun$ tends to lie
along walls, parallel to the vector $\hat{e}_2$; without any clear
trend for alignment/anti-alignment with respec to filaments.

For the angular momentum alignment and the T-web (middle row, right
column) we find no evidence for any alignment at low masses $<10^{12}\hMsun$.
At higher masses $>10^{12}\hMsun$ there is a weak signal
of preferential alignment along the first and second eigenvectors;
between $35\%$ to $45\%$ of the halos are aligned with respect to
$\hat{e}_1$ and $\hat{e}_2$. Correspondingly, between $10\%$ to $20\%$
of the halos are aligned along $\hat{e}_{3}$. This means
that most of the halos are perpendicular to the filaments and do not
have a clear alignment with respect to walls.

The peculiar velocities (lower panels) show a weak but consistent
alignment along the third eigenvector $\hat{e}_{3}$ of the T-web for
all masses below $10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
aligned along the first eigenvector $\hat{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the V-web show the same,
although weaker, trend and only for low mass halos $<10^{12}$.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig2.pdf}
\caption{Median of $|\cos\theta|$ quantifying the shape alignment for
  the V-web (left) and the T-web (right) at two different grid
  resolutions as a function of halo mass.  The errorbars show the $20$ and $80$ percentiles 
  of the distribution; the
  errors on the median are too small to be noticed in this figure. In the upper (lower) panels
  the angle $\theta$ is measured between the halo major axis and the first (third)
  eigenvector.\label{fig:shape_alignment} }
\end{figure*}

@@

In the case of the V-web (left column) we have a clear alignment with
respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
values $\muavg\approx 0.8$ well above the expected value of $0.5$ for a
random distribution. With respect to the third eigenvector we measure
an anti-alignment with $\muavg\approx0.3$. For low masses
$<10^{12}\hMsun$ we do not detect any alignment signal. This is
consistent with the PA results of massive halos
perpendicular to filaments and parallel to walls.

The T-web (right column) shows alignment trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude below than the V-web. In this
case we measure an alignment along the third eigenvector and an
anti-alignment along the first eigenvector. In the latter case at the
highest masses $\muavg\approx 0.8$, while in the former at $\muavg\approx
0.2$. This strong alignment/anti-alignment signal mirrors the
interpretation from the PA results that describe halos lying parallel
both to filaments and walls.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig3.pdf}
\caption{Median of $|\cos\theta|$ quantifying the angular momentum
  alignment for the V-web (left) and the T-web (right) for two different
  grid resolutions as a function of halo mass. In the upper (lower)
  panels the angle $\theta$ is measured between the first (third)
  eigenvector and the angular momentum
  vector.\label{fig:spin_alignment}} 
\end{figure*}

We now focus our attention on the angular momentum alignment. Figure
\ref{fig:spin_alignment} shows the results as a function of halo mass
following the same panel layout as in Figure
\ref{fig:shape_alignment}. In all cases we see that these alignment
trends are weaker than the shape alignments. For the V-web low mass halos
$<10^{12}$\hMsun do not show any preferential alignment with the
cosmic web. Halos more massive than this threshold have their angular
momentum slightly perpendicular to the direction defined by the first
eigenvector and are uncorrelated with the third eigenvector. This translates
into a weak tendency for the angular momentum to lie parallel to walls.

In the case of the T-web, the alignment for low mass halos $<10^{12}$\hMsun
is also absent. More massive halos present a weak alignment along
first eigenvector and anti-alignment with the third eigenvector. This
provides a quantitative expression of the results derived from the
preferential alignment whereby the angular momentum is weakly
perpendicular to filaments.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig4.pdf}
\caption{Median of $\vert\cos\theta\vert$ quantifying the peculiar velocity
  alignment with the V-web (left) and the T-web (right) for two different
  grid resolutions as a function of halo mass. In the upper (lower)
  panels the angle $\theta$ is measured between the first (third)
  eigenvector and a halo's peculiar velocity.
\label{fig:velocity_alignment}}
\end{figure*}

Figure \ref{fig:velocity_alignment} shows the results for peculiar
velocities alignments. In the case of the V-web, the peculiar
velocities show a weak signal of alignment ($\muavg\approx0.55$)
along the third eigenvector for low masses $<10^{12}$\Msun and a weak
anti-alignment at higher masses. The strength of the alignment also shows
a clear dependency on the grid size used to compute the web.

The T-web shows a stronger alignment with the third eigenvector at all
masses with $\muavg\approx0.6$ and an anti-alignment with the first
eigenvector with $\muavg\approx 0.4$. In contrast to the V-web results,
these trends remain basically unchanged at all masses and grid
resolutions, with only minor changes for halos masses $>10^{13}$\hMsun.

@@

Figure \ref{fig:drive} shows the results for the major axes of
the V-web and T-web (left and right panels) and the shape major axis,
the angular momentum vector, and the halo peculiar velocity (top, middle
and bottom panels, respectively).  As here we show the average
of the halo population above the lower mass limit imposed, the halo
masses that dominate the statistics are close to this lower limit $~10^{11}\hMsun$.
We show the result for the T-web and V-web calculated using the two
available resolutions, but as can be seen in general we find no
significant differences in our results.

Halos with higher circularity and inner density show
a higher alignment with the V-web major axes.  The opposite is the case
of haloes with higher concentration, spin and triaxiality.  This trend
is also visible in the angular momentum vs. V-web major axis alignment only
for the concentration and spin, with little differences evidenced by the
other halo properties.  The alignment strengthening is somewhat
reversed when comparing the V-web with the halo peculiar velocity,
with some evidence for a strengthening with lower circularity and
inner density, and a weakening with spin and triaxiality.

On the right panels the trends can also be readily seen.  The T-web
vs. major axis alignments are stronger for higher circularity,
concentration and inner density, and weaker for higher spins and
triaxialities.  With respect to the angular momentum, the alignment
is weaker for higher circularities, concentrations, inner densities and
spins, and is only strengthened when the triaxiality is higher.
Not much difference is seen in the T-web vs. halo peculiar velocity
alignments, being this the only regime where there is a clear difference
in influence of halo properties on the alignments with the T-web and V-web;
the latter do show important changes on the lower-left panel.

As can be seen, higher concentrations, circularities and densities,
as well as lower spins and triaxialities, produce a similar effect on the
T-web vs. major axis alignments to that of diminishing the mass
of the halos.  This has also been detected in other halo properties such
as their clustering amplitude in what has been termed assembly bias
\citep[][e.g.]{Gao2005,Li2008,Lacerna2011} where halos of different
ages and equal mass show different clustering amplitudes, which could
also be interpreted as a change in the effective halo mass according
to halo properties.

An older halo age has been shown to come along with more spherical halo
shapes, higher concentrations and halo inner density.  However, in the
assembly bias scenario of \cite{Gao2005}, these halos tend to show a clustering
amplitude consistent with that of the median halo population of higher masses.
In terms of the alignments with the T-web, our results show the opposite
trend.  This shows that the physics behind the clustering amplitude and
alignments do not necessarily coincide.  The full understanding of
the dependence of halo properties and/or on their environment is
a complex problem, but these results provide extra information that complements
that obtained from clustering measurements.

@@

For the two algorithms, T-web and V-web, we have the information for their
eigenvectors and eigenvalues on exactly the same positions defined
by the grids. This allows us to compute the pair-wise alignment
between the eigenvectors in the two web finders.

@@

Figure \ref{fig:interweb} shows the values for $\muavg$ between the
two $\hat{e}_1$ eigenvectors in the T-web and the V-web.  The Figure
shows that there is an alignment, $\muavg\approx 1.0$, for low mass
halos and an anti-alignment, $\muavg\approx 0.2$ for massive ones.

@@

We have examined the alignment of shape, angular momentum and peculiar
velocity of dark matter halos with respect to the cosmic web. We use
publicly available data from two algorithms implemented on a large
cosmological N-body simulation to study halo populations spanning five
orders of magnitude in mass. The first algorithm uses the tidal field (T-web)
and the second the velocity shear (V-web); both include results on
spatial scales of $0.5$\hMpc and $1.0$\hMpc.

We quantify the alignments in two complementary ways. The first one
measures the fraction of halos in a population that is preferentially
aligned with either one of the eigenvectors $\hat{e}_1$, $\hat{e}_2$
or $\hat{e}_3$ in the local definition of the cosmic web. The second
method measures the average value of the angle between an eigenvector
and the vector of interest. These two measurements give us a
complete picture for the different degrees of alignment in the web.

We find that the strongest alignment occurs for the halo shape with
respect to the T-web. In this case the halos tend to align with the
third eigenvector, $\hat{e}_3$, meaning that they lie along filaments
and walls. This trend gets stronger as the halo mass
increases and agrees with all the results published so far. Instead,
for the momentum based V-web, there is only an anti-alignment for halos
more massive than $10^{12}\hMsun$, a result that is presented here for
the first time.

A much weaker alignment signal is present for the angular momentum. In
the T-web only the most massive halos $>10^{12}$\hMsun are
perpendicular with respect to $\hat{e}_3$ (anti-aligned to filaments),
while for the V-web the massive halos are aligned with $\hat{e}_2$,
lying along sheets. These results broadly agree with the
published literature. Nevertheless, in some publications
\citep{AragonCalvo2007,Hahn2007,AragonCalvo2014} there is an alignment signal
reported at lower halo masses $<10^{12}$\hMsun that we do not detect
in our measurements. Actually \cite{AragonCalvo2014}, using a
multiscale web-finding method, confirmed the mass $10^{12}$\hMsun as a
transitional scale between alignment /anti-alignment in filaments,
showing that it reflects the degree of evolution of the host
filament.

@@

A new result from our study is the alignment for the peculiar
velocities. Here we find a relatively strong signal of alignment along
the direction defined by the third eigenvector, $\hat{e}_3$, and
perpendicular to the first, $\hat{e}_1$. This signal is clear in the
T-web for all masses below $<10^{13}$\hMsun. This can be interpreted as
a flow parallel to walls and filaments. In the case of the V-web
similar signal, albeit weaker, is present only for the low mass halos
$<10^{12}\hMsun$. A similar result was obtained by \citep{Padilla2005}
who found that peculiar velocities are larger in the direction
parallel to void walls.

The different behaviour for the alignments of massive halos in the
T-web and the V-web is explained by an anti-alignment between the
eigenvectors in the two web grids for massive halos
$>10^{12}\hMsun$. For low mass halos the directions defined by the two
webs point in the same direction. This trends can be interpreted as
non-linear effects that appear in the two different physical
descriptions for the cosmic web, but the impact of the numerical
choices to build the interpolation must be studied as well.

We also performed a simple study to find evidence of halo properties,
other than mass, in driving the alignments. We find that in the case of
shape, high concentration halos or halos with a low value of
the reduced spin parameter tend to show a stronger signal. This trend is
more pronounced in the T-web than in the V-web. Concerning angular
momentum we find that the anti-alignment signal is stronger for halos
with high spin values. In the peculiar velocities we do not find any
effect in the T-web alignments, and the results for the V-web show 
wide variations with grid resolution that impedes driving any strong
conclusion.
